Combined Task and Motion Planner through an Interface Layer

### 2015-05-12 documentation/ps4.tex
fixed compile error

\begin{figure}
\begin{tabular}[t]{|l|l|l|l|l|l|l|}\extrarowheight
\hline

Shape & Blocks & \shortstack{Goal Number of\\Blocks to Move} & Obstructions & \shortstack{Motion Planner\\Calls} & \shortstack{Task Planner\\Calls} & Runtime \\ \hline
Square & 9 & 56 &  & ? & ?&\\
\hline
Sorting & 9 & 56 & ? & ? & ?&\\
\hline

>>>>

\begin{figure}
\begin{tabular}[t]{|l|l|l|l|l|l|l|}
\hline

Shape & Blocks & \shortstack{Goal Number of\\Blocks to Move} & Obstructions & \shortstack{Motion Planner\\Calls} & \shortstack{Task Planner\\Calls} & Runtime \\ \hline
Square & 9 & 56 & ? & ? & ?& ? \\
\hline
Sorting & 9 & 56 & ? & ? & ?& ?\\
\hline
